Interactive Visualization for System Log Analysis

### 2013-12-17 paper/paper.tex
Updated intro and abstract

In this paper we present the way of visualizing large amount of system log data into single screen.
These log files from distributed systems can be tens of or hundreds of megabytes, and impossible to
parse without tools. Due to the amount of data we cluster machines by similar trends and also
pre-process the data in order to achieve real-time clustering according to user inputs. By doing so
we end up separating actual anomalous nodes from normal ones and can show the information in
visualization clearly.

@@

\section{Introduction}
% An explanation of the problem and the motivation for solving it.

The gears of a distributed system are constantly moving, and the system administrator uses log files
to understand what goes on underneath. They are also spread out over many machines and many places in
these machines.

Our goal is to aggregate this data into a visualization that can be easily checked by the system
administrator. It should take no more than a glance to understand the system state, failures, or any
other desired information. This will allow the system administrator to regularly check the state
without setting up special scripts which parse the logs. For example, the system administrator
should be able to view the progress of a task while away from the office and without access to a
command-line.

The research problem is figuring out how to display megabytes of log data into a visually and
interactively simple interface and spot abnormalities without any additional effort.

@@

\section{Related Works}
% A description of previous papers related to your project.

>>>>

We present a visualization interface to assist system administrators in searching system logs.
Even with current regular expression matchers such as \texttt{grep}, the amount of log data is difficult for humans to understand.
We augment \texttt{grep} with a visualization of the matched patterns.
To further reduce the amount of information displayed, we cluster similarly-performing nodes and only show a single node representative of the entire cluster.
The user can then interactively search the log, zoom in on a certain time window, and choose the number of clusters.
%This means that at the most ``zoomed out'' state (no time window specified, no search patters, and no clustering), the raw log data is displayed.
Our simulations show that our clustering is effective and our system is fast:
the clustering successfully isolates anomalously-performing nodes in a variety of situations;
the visualization can interactively visualize hundreds of millions of log messages across a hundred nodes in real-time.
TODO: Get the numbers from this simulation.

@@

\section{Introduction}

The gears of a distributed system are complex and constantly moving.
A system administrator uses log files to understand the underlying structure and detect anomalous behavior.
These logs are large, distributed across many filesystems, and hard to understand even with today's tools.

Our goal is to aggregate the log data into a visualization that can be easily understood by the system administrator.
The two primary use cases are:
\begin{enumerate}
\item searching through system logs to find software bugs or hardware failures, and
\item viewing the current system state on-the-go without access to a command line.
\end{enumerate}
To this end, our system contributes the following features:
\begin{enumerate}
\item \textbf{trustable}: the user is able to view the raw data at the most ``zoomed out'' state;
\item \textbf{fast and distributed}: the proprocessing primarily occurs at each node, with a single central node aggregating preprocessed data; and
\item \textbf{interactive}: the user can adjust the paramaters of the visualization at interactive speeds.
\end{enumerate}

@@

\section{Related Work}
% A description of previous papers related to your project.
